\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
%Template version as of 6/27/2024

\input{paper_preamble}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Putting Software Testing Terminology to the Test\\
    % Sub-titles should not be used!
    \ifblind{\thanks{Funding information suppressed.\vspace{4mm}}}
    {\thanks{Funding for this work was provided by the Ontario Graduate
            Scholarship and McMaster University.}
    }
}

\author{
    \ifblind{Author details suppressed\vspace{18mm}}
    {\IEEEauthorblockN{Samuel J. Crawford\IEEEauthorrefmark{1},
            Spencer Smith\IEEEauthorrefmark{1}, Jacques Carette\IEEEauthorrefmark{1}}
        \IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Computing and Software \\
            McMaster University\\
            Hamilton, Canada \\
            \{crawfs1, smiths, carette\}@mcmaster.ca}}}

% % Previous version (weird formatting)
% \newcommand{\deptCAS}[1]{
%     \IEEEauthorblockA{\textit{Department of Computing and Software} \\
%         \textit{McMaster University}\\
%         Hamilton, Canada \\
%         #1@mcmaster.ca}}

% \author{\IEEEauthorblockN{Samuel~J.~Crawford}
%     \deptCAS{crawfs1}
%     \and
%     \IEEEauthorblockN{Spencer~Smith}
%     \deptCAS{smiths}
%     \and
%     \IEEEauthorblockN{Jacques~Carette}
%     \deptCAS{carette}
% }

\maketitle

\begin{abstract}
    Testing is a pervasive software development activity that is often
    complicated and expensive (if not simply overlooked), partly due to
    the lack of a standardized and consistent taxonomy for software testing.
    This hinders precise communication, leading to discrepancies and
    ambiguities across the literature and even within individual documents!
    % Therefore, automating the software testing process is an area of interest,
    % and understanding the underlying domain is an important prerequisite.
    In this paper, we systematically examine the current state of software
    testing terminology. We 1) identify established standards
    and prominent testing resources, 2) capture relevant testing terms
    from these sources, along with their definitions and relationships---both
    explicit and implied---and 3) construct graphs to visualize and analyze
    this data. Our research uncovered more than 500 test approaches and
    four methods for describing ``implied'' test approaches. We also build
    a tool for generating graphs that illustrate relations between test
    approaches and track ambiguities captured by this tool and
    manually through the research process. Our results reveal 127 discrepancies
    or ambiguities, including ten terms used as synonyms to two (or more)
    disjoint test approaches and 14 pairs of test approaches may either be
    synonyms or have a child-parent relationship. Confusion was notable
    around functional, recovery, scalability, and performance testing,
    along with 45 other discrepancies. These findings make clear the urgent
    need for improved testing terminology so that the discussion, analysis and
    implementation of various test approaches can be more coherent. We
    provide some preliminary advice on how to achieve this standardization.
\end{abstract}

\begin{IEEEkeywords}
    Software testing, terminology, taxonomy, literature review, test approaches
\end{IEEEkeywords}

\section{Background}

% TODO: tighten up, add sources

Testing software is complicated, expensive, and often overlooked.
Improving the productivity of testing and testing research requires a standard
language for communication. Unfortunately, a search
for a systematic, rigorous, and ``complete'' taxonomy for software testing
revealed that the existing ones are inadequate:

\begin{itemize}
    \item Tebes et al. \cite{TebesEtAl2020a} focus on \emph{parts} of the
          testing process (e.g., test goal, testable entity),
    \item Souza et al. \cite{SouzaEtAl2017} prioritize organizing testing
          approaches over defining them, and
    \item Unterkalmsteiner et al. \cite{UnterkalmsteinerEtAl2014} provide a
          foundation for classification but not how it applies to software
          testing terminology.
\end{itemize}

Thus we set about closing this gap. We first define the scope of what kinds of
``software testing'' are of interest (\Cref{scope}) and examine the existing
literature (\Cref{method}). This reinforces the need for a proper taxonomy!
Despite the amount of well understood and organized knowledge (\Cref{observ}),
there are still many discrepancies and ambiguities in the literature, either
within the same source or between various sources (\Cref{discrep}). We provide
some potential solutions covering some of these discrepancies (\Cref{recs}).

\input{chapters/03e_scope}
\input{chapters/03b_methodology}
\input{chapters/03c_observations}
\input{chapters/03d_discrepancies}
\input{chapters/03f_recommendations}

\section{Conclusion}

While a good starting point, the current literature on software testing has
much room to grow. The many ambiguities and confusions create unnecessary
barriers to software testing. While there is merit to allowing the state-of-%
the-practice terminology to descriptively guide how terminology is used, there
may be a need to prescriptively structure terminology to intentionally
differentiate between and organize various test approaches. Future work in this
area will continue to investigate the current use of terminology, in
particular \nameref{undef-terms}, determine if IEEE's current
\nameref{categories-observ} are sufficient, and rationalize the definitions of
and relations between terms.

\section*{Acknowledgment}

ChatGPT was used for proofreading and assistance with \LaTeX{} formatting and
supplementary Python code for constructing graphs and generating \LaTeX{} code,
including regex. \ifblind{}{Jason Balaci's
    \href{https://github.com/balacij/McMaster-Thesis-Template}
    {McMaster thesis template} provided many helper \LaTeX{} functions.}

\newpage

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}

\end{document}
