\ifnotpaper\section{Tools}
\else\subsection{Tools}
\fi\label{tools}

\ifnotpaper
    To better understand our findings, we build tools to more intuitively
    visualize relations between test approaches (\Cref{app-rel-vis}) and
    automatically track their flaws (\Cref{flaw-analysis}). Doing
    this manually would be error-prone due to the amount of data involved (for
    example, we identify \approachCount{} test approaches) and the number of
    situations where the underlying data would change, including more detailed
    analysis, error corrections, and the addition of data. These all require
    tedious updates to the corresponding visualizations that may be overlooked
    or done incorrectly, so automating these processes allows for our results
    to be reproduced (by us or others) and account for new data. Besides being
    more systematic, this also allows us to observe the impacts of smaller
    changes, such as unexpected flaws that arise from a new relation between
    two approaches. It also helps verify the tools themselves; for example,
    tracking a flaw manually should affect relevant flaw counts, which we can
    double-check. We also define \LaTeX{} macros to help achieve our goals of
    maintainability, traceability, and reproducibility (\Cref{macros}).

    \subsection{Approach Relation Visualization}\label{app-rel-vis}
\fi

To better understand the relations between test approaches, we develop a tool
to generate visualizations of these relations automatically.
\ifnotpaper
    % We can describe these graphs formally as ordered triplets
    %     $G = (A, S, P)$, where:  % Format based on https://en.wikipedia.org/wiki/Graph_theory
    %     \begin{itemize}
    %         \item $T$ is the set of terms assigned to test approaches by the
    %               literature,
    %         \item $A \subseteq T$ is a subset of the \approachCount{} test
    %               approaches we record as rows in \ourApproachGlossary{} that
    %               function as the vertices of the graph,
    %         \item $S \subseteq \left\{ \{x, y\} \mid x, y \in T \,\textrm{ and }\,
    %                   (x \in A \,\textrm{ or }\, y \in A) \,\textrm{ and }\, x \neq y \right\}$
    %               is a subset of our identified synonym relations (defined
    %               in \Cref{syn-rels}) that function as edges, and
    %         \item $P \subseteq \left\{(x,y) \mid (x, y) \in A^2 \right\}$ is a
    %               subset of our identified parent-child relations (defined in
    %               \Cref{par-chd-rels}) that also function as edges.
    %     \end{itemize}
    Since we use a consistent format to track synonym and parent-child
    relations (defined in \Cref{syn-rels,par-chd-rels}, respectively)
    between approaches in \ourApproachGlossary{}, we can parse them
    systematically. For example, if the entries in \Cref{tab:exampleGlossary}
    appear, then their parent-child relations are visualized as
    shown in \Cref{fig:exampleGraph}. We also capture relevant
    citation information in our glossary in the author-year citation format,
    ``reusing'' information from previous citations when applicable.
    For example, the first row of \Cref{tab:exampleGlossary}
    contains the citation ``(Author, 2022; 2021)'', which means that this
    information was present in two documents by Author: one written in
    2022 and one in 2021. The following citation, ``(2022)'',
    contains no author, which means it was written by the same one as the
    previous citation (Author). We process these citations according to this
    logic \seeSrcCode{231bd5e}{scripts/csvToGraph.py}{54}{95} so we can
    consistently track them throughout our analysis.

    \input{build/exampleGlossary.tex}
    \ExampleParChdGraphs{}

    \clearpage\fi
\phantomsection{}\label{relevantSyns}
Overall, the parent-child relations between test approaches \emph{should}
result in a hierarchy (or multiple discrete hierarchies), but due to flaws in
the literature such as self-loops (see \Cref{selfParDef}), this is not the
case. Therefore, we visualize all parent-child relations as they are guaranteed
to be meaningful.
% , but only graph some synonym relations.
% For a given synonym pair to
% be captured by our methodology, at least one term will have its own row in its
% relevant glossary.
However, since each term is trivially a synonym of itself and there are many
non-problematic synonyms that do not imply flaws (see \Cref{syn-rels}),
we only visualize the following synonym relations, which may indicate flaws:

% We then decide whether to include or exclude the synonym
% pair from our generated graphs based on the following possible cases:
\begin{enumerate}
    % \item[1. (Excluded)] \phantomsection{}\label{syn-case-one}
    %       \hfill \ifnotpaper
    %           $\left\{ \{x, y\} \in S \mid x \in A \,\textrm{ xor }\, y \in A \right\}$
    %       \fi \break
    %       \textbf{Only one synonym has its own row.}
    %       This is a ``typical'' synonym relation (see \Cref{syn-rels}) where
    %       the terms are interchangeable. We \emph{could} include the synonym
    %       as an alternate name inside the node of its partner, but we do not
    %       want to clutter our graphs unnecessarily.

    \item%[2. (Included)] \phantomsection{}\label{syn-case-two}
          %   \hfill \ifnotpaper
          %       $\left\{ \{x, y\} \in S \mid x, y \in A \right\}$
          %   \fi \break
          \textbf{Synonyms between approaches defined independently.}\hfill\break
          If two separate approaches have their own definitions, nuances,
          etc.~but are also labelled as synonyms, this may indicate that the
          two terms are interchangeable and could be merged \emph{or} that
          either their definitions or this synonym relation is incorrect.
          % TODO: pretty hacky
          % into one row, which would result in \hyperref[syn-case-one]{Case 1} above.

    \item%[3. (Included)] \phantomsection{}\label{syn-case-three}
          %   \hfill \ifnotpaper
          %       $\left\{ \{x, z\}, \{y, z\} \in S \mid x, y \in A \,\textrm{ and }\,
          %           z \notin A \right\}$
          %   \fi \break
          \textbf{Synonyms that violate transitivity.}\hfill\break
          If two distinct approaches share a synonym, that implies that they
          are synonyms themselves. If they are \emph{not}, one or more
          relations may be incorrect or missing.
\end{enumerate}
\ifnotpaper
    We deduce these conditions from the information we parse from our glossary.
    For example, if the entries in \Cref{tab:synExampleGlossary} appear, then
    they are visualized as shown in \Cref{fig:exampleSynGraph} (note that X
    does not appear since it is not defined independently and does not violate
    transitivity).

    \input{build/synExampleGlossary.tex}
    \ExampleSynGraph{}

    \phantomsection{}\label{visExplicit}
    Since we also track the ``explicitness'' of information (defined in
    \Cref{explicitness}), we can represent explicit \emph{and} implicit
    relations without double counting them during the analysis in
    \Cref{flaw-analysis}. If a relation is both explicit \emph{and} implicit,
    we only display the implicit relation if its source is from a more
    credible source tier (see \Cref{cred,source-tiers}). For example, if
    ``StdAuthor'' from \Cref{tab:synExampleGlossary} is an author of an
    established standard, then we display the implicit relation from their
    document alongside the explicit one from ``Author'' as shown in
    \Cref{fig:exampleSynGraph}.
    % For example, only the explicit synonym relation between E and F
    % from \Cref{tab:exampleGlossary} appears in \Cref{fig:synExampleGraph}.
    Implicit approaches and relations are denoted by dashed lines, as shown in
    \Cref{fig:exampleGraph,fig:exampleSynGraph}, while explicit approaches are
    \emph{always} denoted by solid lines, even if they are also implicit. We
    can also generate ``explicit'' versions of these visualizations that exclude
    implicit approaches and relations; for example, \Cref{fig:expExampleGraph}
    is the explicit version of \Cref{fig:exampleGraph}%, and
    % \Cref{fig:expSynGraph} likewise only contains explicit approaches and
    % synonym relations
    .

    We also colour each relation according to its source tier, including
    inferences (see \Cref{infers}) and proposals (see \Cref{recs}). For
    clarity, we only display the relation with the most credible source tier
    (except if there is a more credible implicit relation as we previously
    describe). Each source tier gets its own colour that we include in the
    legend for each visualization (such as \Cref{fig:exampleSynGraph}),
    although we omit this colouring from \Cref{fig:exampleParChdGraphs,%
        fig:exampleFlawGraphs} for clarity.

\fi
These visualizations tend to be large, so it is often useful to focus on
specific subsets of them. \ifnotpaper For each approach category (defined in
    \Cref{cats-def}), we generate a visualization restricted to its approaches
    and the relations between them. We also generate a visualization of all static
    approaches along with the relations between them \emph{and} between a
    static approach and a dynamic approach. This static-focused visualization is
    notable because static testing is sometimes considered to be a separate
    approach category (see \flawref{static-test-flaw}). Since dynamic
    approaches are our primary focus (see \Cref{static-test}), we include them
    in this static visualization, colouring their nodes grey to distinguish them.
    %, as in \Cref{fig:staticExampleGraph}, 

    We can also \else We can \fi generate more focused visualizations from a
given subset of approaches, such as \ifnotpaper\else those in a selected
    approach category (defined in \Cref{cats-def}) or \fi those pertaining to
recovery or scalability\ifnotpaper.
% These areas are of particular note as we discuss their
% flaws in their own sections (\Cref{recov-flaw,scal-flaw}, respectively).
We use these visualizations to better understand the relations within these
subsets of approaches, but we can also update them based on
our recommendations by specifying sets of approaches and relations to add or
remove. % given \else; the latter are shown \fi
% in \Cref{fig:rec-graph-current,fig:scal-graph-current}, respectively.
% applying those given in \Cref{rec-test-rec,,scal-test-rec,,\ifnotpaper\else%
%         perf-test-rec\fi} results in the updated graphs in
% \Cref{fig:rec-graph-proposed,,fig:scal-graph-proposed,,\ifnotpaper\else%
%         fig:perf-graph\fi}, respectively.
When doing so\ifnotpaper\ in \Cref{recs}\fi, we colour any added approaches or
relations orange to distinguish them.
% \ifnotpaper
% Recommendations can also be inherited; for example, we generate
% \Cref{fig:perf-graph} based on the modifications we apply to
% \Cref{fig:rec-graph-proposed,fig:scal-graph-proposed} and
% other changes from \Cref{perf-test-rec}. \fi

\input{chapters/04a_flaw_analysis}
\else
% Moved here to display nicely in paper
\flawMnfstsTable{}
\flawDmnsTable{}
\fi
